\Huge Handwritten digit recognition

### 2017-02-08 doc/Paper.tex
Add plots, b&w model graph

\begin{tikzpicture}
\centering
\begin{axis} [
  title={Training performance},
  xlabel={Epoch},
  ylabel={Accuracy (\%)},
  xmin=0, xmax=100,
  ymin=0, ymax=100,
  xtick={0,25,50,75,100},
  ytick={0,25,50,75,100},
  legend pos=south east,
]

\addplot[]
  coordinates {
  (0,25)(25,65)(50,90)(100,95)
  };
\addplot[dashed]
  coordinates {
  (0,25)(25,50)(50,80)(100,90)
  };

\legend{train set, test set}
\end{axis}
\end{tikzpicture}

@@

>>>>

\begin{center}
\begin{tikzpicture}
\begin{axis} [
  title={Training performance},
  xlabel={Epoch},
  ylabel={Accuracy (\%)},
  xmin=0, xmax=100,
  ymin=0, ymax=100,
  xtick={0,25,50,75,100},
  ytick={0,25,50,75,100},
  legend pos=south east,
  axis line style={black!65, line width=.1pt}, % thinner frame border
  legend style={draw=black!50, line width=.1pt}, % thinner frame border
  every x tick/.style={white}, % hide x ticks (make them white)
  every y tick/.style={white}, % hide y ticks (make them white)
  every axis plot/.append style={thick},
]

\addplot[]
  coordinates {
  (0,25)(25,65)(50,90)(100,95)
  };
\addplot[dash pattern=on 6pt off 4pt]
  coordinates {
  (0,25)(25,50)(50,80)(100,90)
  };

\legend{train, test}
\end{axis}
\end{tikzpicture}
\end{center}

@@

\begin{center}
\begin{tikzpicture}
\begin{axis}[
  title={Time performance},
  xlabel=Processes,
  ylabel=Seconds,
  bar width=.8cm,
  axis line style={black!65, line width=.1pt}, % thinner border
  symbolic x coords={1,2,4,6,8,12,16}, % equidistant bars
  every x tick/.style={white}, % hide x ticks (make them white)
  every y tick/.style={line width=.1pt, draw=gray!10}, % y ticks same color as grid
  ymajorgrids=true, % show horizontal grid lines
  grid style={line width=.1pt, draw=gray!10}, % gray grid lines
  ]
  \addplot[ybar, black!40, fill=black!20] coordinates {
      (1,8) 
      (2,5)
      (4,4) 
      (6,3) 
      (8,2.5) 
      (12,2) 
      (16,1.5)    
      };
\end{axis}
\end{tikzpicture}
\end{center}
